A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-21 paper.tex
merge

 && \multirow{2}*{\hyperref[cor:3dN8Btwist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\

@@

 && \multirow{2}*{\hyperref[cor:3dN8Atwist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\RR^3_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline

@@

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\Sect(\CC^3, (U\otimes K_{\CC^3}^{1/2}) \ham \fg)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\Sect(\CC^2 \times \RR_{\mr{dR}}, (U\otimes K_{\CC^2}^{1/2}) \ham \fg)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Sect}(\CC^2, U \ham \fg)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
 &&& $\Sect(\CC \times \RR^2_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Sect}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
 &&& $\map(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_8}
\end{table}

@@

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we will denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sect:susyalgebras}.

@@

\begin{prop} \label{prop:susydimlred}
Suppose $(E, \omega, S)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$. Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*S^{(i)}_{V_\RR} = S^{(i)}_{W_\RR}$.
\end{prop}

\begin{proof}
This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, \omega, S)$ to auxiliary fields generated by the representation $\Sigma$.
\end{proof}

@@

\begin{prop}
Fix a square-zero supercharge $Q$ and a compatible homomorphism $\alpha\colon \U(1)\rightarrow G_R$. Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
\label{prop:twistdimensionalreduction}
\end{prop}

@@

We will now construct an $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $S_{\gauge}^{(1)}, S_{\gauge}^{(2)}, \dots$, where $S_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $S_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align}
S_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
S_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right). \label{eq:gaugeI2}
\end{align}

@@

\begin{theorem}
Fix the homomorphism $\alpha = \alpha_n$. The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$. Moreover, the equivalence is $\MU(2)$-equivariant.
\label{thm:4d2holomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varsigma . \\
\end{align*}

@@

\section{Dimension 3}
The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.  The maximal supersymmetric gauge theory has $\mc N=8$.  There are $\mc N=4$ super Yang--Mills theories for every choice $U$ of a complex symplectic representation of the gauge group, and $\mc N=2$ super Yang--Mills theories for every choice $R$ of arbitrary complex representation of the gauge group. Finally, there are $\cN=1$ super Yang--Mills theories in 3 dimensions, but there are no square-zero supercharges with that amount of supersymmetry. In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.

\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang--Mills Theory}
\label{sect:3d_2_section}

Fix a gauge group $G$ and a representation $R$.  The 3d $\mc N=2$ super Yang--Mills theory arises by dimensional reduction from 4d $\mc N=1$ super Yang--Mills theory with an $R$-valued chiral multiplet.  In this case, $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing. The R-symmetry group is $G_R=\CC^\times$, acting on $W$ with weights $1$ and $-1$.

This theory admits a unique twist up to equivalence:
\begin{itemize}
 \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.  There is a twisting homomorphism $\phi = \MU(1)\cong \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action. The twist is $\ZZ$-graded.
\end{itemize}

\subsubsection{Minimal Twist}
\label{sect:3dminimaltwist}
A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$. We use the twisting homomorphism $\phi\colon \MU(1)\xrightarrow{\det^{1/2}} \U(1)\hookrightarrow G_R$.

@@

\begin{theorem} \label{3d_minimal_twist_thm}
The minimal twist of the 3d $\cN=2$ super Yang--Mills theory with Lie algebra $\fg$ with matter valued in a $\fg$-representation $R$ is perturbatively equivalent to the generalized BF theory with the space of fields $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

\begin{proof}
By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$. By Proposition \ref{prop:BFholomorphicreduction} we get that the dimensional reduction of the holomorphic BF theory on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the holomorphic BF theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
Next, consider the 3d $\mc N=4$ supersymmetric Yang--Mills theory with matter valued in a symplectic $G$-representation $U$. The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the vector representation.

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  
 In this case $Q$ is minimal, with 2 invariant directions.  
 Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence. They admit a twisting homomorphism and a $\ZZ$-grading.
 \item Rank 2. Such supercharges are topological.  
A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  
The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation. We refer to these as the $A$-twist and the $B$-twist, distinguished by whether they admit a $\ZZ$-grading:
\begin{enumerate}
\item
An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
\item
A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
This twist is only $\ZZ/2\ZZ$-graded.
\end{enumerate}
\end{itemize}

@@

\begin{lemma} \label{3d_4_orbits_lemma}
A rank $(2,0)$ square-zero supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.  Likewise, a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
\end{lemma}

\begin{proof}
Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.  
This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.  This supercharge admits a compatible homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor. This is the $A$-twist in our classification above.

A rank $(1,1)$ supercharge induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.  This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.  
\end{proof}

\subsubsection{Minimal Twist}
\label{sect:3d_4_minimal_twist}
There is a unique twisting homomorphism $\phi \colon \MU(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\MU(1) \subset \MU(2)$.

To incorporate the $\ZZ$-grading, we use the homomorphism $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$. This homomorphism coincides with the dimensional reduction of $\alpha_0$ from Section \ref{sect:4d_2_holomorphictwist}. The corresponding $\U(1)$-action on the 3d auxiliary space $W$ under $\alpha$ coincides with the $\U(1)$-action on the 4d auxiliary space $W_4$ under the isomorphism $W\cong W_4\oplus W_4^*$. Indeed, both have weights $(1,1,-1,-1)$.  Therefore, our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.  Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.

>>>>

 && \multirow{2}*{\hyperref[sect:3d8B_Twist] {Rank $2$ (B)}} & {BF Theory } & \multirow{2}*{3 (topological)} \\

@@

 && \multirow{2}*{\hyperref[sect:3d8A_Twist] {Rank $2$ (A)}} & {Perturbatively trivial} & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Map}(\CC_{\mr{Dol}} \times \RR_{\mr{dR}}, \gg/\gg)_{\mr{dR}}$ & \\ \hline

@@

\begin{table}[!ht]
 \centering
 \begin{tabular}{c|c|c|c|c}
 $d$ & $\mc N$ & Twist & Description & Invariant Directions \\
 \hline
 \multirow{2}*{6} & \multirow{2}*{$(1,0)$} & \multirow{2}*{\hyperref[sect:6dholomorphictwist]{Rank $(1,0)$}} & {Holomorphic BF Theory coupled to a holomorphic symplectic boson} & \multirow{2}*{3 (holomorphic)} \\
 &&& $\Sect(\CC^3, (U\otimes K_{\CC^3}^{1/2}) \ham \fg)$ & \\ \hline
 \multirow{2}*{5} & \multirow{2}*{$1$} & \multirow{2}*{\hyperref[sect:5d1minimaltwist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3 (minimal)} \\
 &&& $\Sect(\CC^2 \times \RR_{\mr{dR}}, (U\otimes K_{\CC^2}^{1/2}) \ham \fg)$ & \\ \hline
 \multirow{6}*{4} & \multirow{6}*{$2$} & \multirow{2}*{\hyperref[sect:4d_2_holomorphictwist] {Rank $(1,0)$}} & {Holomorphic BF Theory} & \multirow{2}*{2 (holomorphic)} \\
 &&& $T^*[-1]\mr{Sect}(\CC^2, (U \otimes K_{\CC^2}^{1/2}) \ham \fg)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d_2_11] {Rank $(1,1)$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{3} \\
 &&& $\Sect(\CC \times \RR^2_{\mr{dR}}, (U\otimes K_\CC^{1/2}) \ham \fg)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:4d2Donaldson] {Rank $(2,0)$}} & {Perturbatively trivial } & \multirow{2}*{4 (topological)} \\
 &&& $\mr{Sect}(\CC^2, U \ham \fg)_{\mr{dR}}$ & \\ \hline
 \multirow{6}*{3} & \multirow{6}*{$4$} & \multirow{2}*{\hyperref[sect:3d_4_minimal_twist] {Rank $1$}} & {Generalized BF Theory coupled to a generalized symplectic boson} & \multirow{2}*{2 (minimal)} \\
 &&& $T^*[-1]\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)$  & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_B_twist] {Rank $2$ (B)}} & {BF Theory coupled to a symplectic boson} & \multirow{2}*{3 (topological)} \\
 &&& $\map(\RR^3_{\mr{dR}}, U \ham \fg)$ & \\ \cline{3-5}
 && \multirow{2}*{\hyperref[sect:3d_4_A_twist] {Rank $2$ (A)}} & {Perturbatively trivial } & \multirow{2}*{3 (topological)} \\
 &&& $\mr{Sect}(\CC \times \RR_{\mr{dR}}, U \ham \fg)_{\mr{dR}}$ & \\ \hline
  \end{tabular}
 \caption{Twists of Supersymmetric Yang-Mills Theories with gauge Lie algebra $\fg$ with a hypermultiplet valued in a symplectic representation $U$ (8 supercharges).}
 \label{table_of_twists_8}
\end{table}

@@

Fix a spinorial representation $\Sigma$ of $\so(V)$, a nondegenerate pairing $\Gamma_V\colon \sym^2(\Sigma)\rightarrow V$ and a group of $R$-symmetries $G_V$.  This datum generates a supersymmetry algebra, which we'll denote by $\mf A$.  We have a natural embedding
\[\so(W)\oplus \so(W^{\perp})\subset \so(V),\]
so $\Sigma$ restricts to a spinorial $\so(W)$ representation. We define the dimensionally reduced $\Gamma$-pairing as the composite
\[\Gamma_W\colon \sym^2(\Sigma)\xrightarrow{\Gamma_V} V\rightarrow W,\]
where the last map is the orthogonal projection onto $W$. Finally, we have a new $R$-symmetry group
\[G_W = G_V\times \Spin(W^\perp_\RR).\]
This datum generates a supersymmetry algebra $\mf A'$ in dimension $\mr{dim}(W_\RR)$ as defined in Section \ref{sect:susyalgebras}.

@@

\begin{prop} \label{prop:susydimlred}
Suppose $(E, Q, \omega, I)$ is an $\mf A$-supersymmetric classical field theory on $V_\RR$. Then its dimensional reduction along the projection $p\colon V_\RR\rightarrow W_\RR$ has a unique $\mf A'$-supersymmetric structure, compatible with the supersymmetry on $V_\RR$ in the sense that $p^*I^{(i)}_{V_\RR} = I^{(i)}_{W_\RR}$.
\end{prop}

\begin{proof}
This follows from the proof of Proposition \ref{prop:dimensionalreductionunique} by coupling the theory $(E, Q, \omega, I)$ to auxiliary fields generated by the representation $\Sigma$.
\end{proof}

@@

\begin{prop}
Fix a twisting datum $(Q, \alpha)$, where $\Gamma_V(Q, Q) = 0$. Then the dimensional reduction of the twist of the classical field theory $E$ is isomorphic to the twist of the dimensional reduction of $E$.
\label{prop:twistdimensionalreduction}
\end{prop}

@@

We will now construct an elliptic $L_\infty$ action of the super Lie algebra $\mf{A}$ on the theory. Following Definition \ref{infinitesimal_action_def}, we have to prescribe a collection of functionals $I_{\gauge}^{(1)}, I_{\gauge}^{(2)}, \dots$, where $I_{\gauge}^{(k)}\colon \mf{A}^{\otimes k}\rightarrow \oloc(\cE)$, together satisfying the classical master equation. The supersymmetry action we construct will extend the Poincar\'{e} action from \eqref{eq:YMPoincareaction}, so we just have to specify the values of $I_{\gauge}^{(k)}$ on the supersymmetry generators in $\Sigma$. The action of supersymmetry is given by a linear and a quadratic functional
\begin{align}
S_{\gauge}^{(1)}(Q) &= \int_{V_\RR}\dvol\left( -(\Gamma(Q, \lambda), A^*) + \frac{1}{2}(\rho(F_A)Q, \lambda^*)\right) \label{eq:gaugeI1} \\
S_{\gauge}^{(2)}(Q_1, Q_2) &= \int_{V_\RR}\dvol\left( \frac{1}{4}(\Gamma(Q_1, Q_2), \Gamma(\lambda^*, \lambda^*)) - \frac{1}{2}(Q_1, \lambda^*)(Q_2, \lambda^*) - \iota_{\Gamma(Q_1, Q_2)} A c^*\right). \label{eq:gaugeI2}
\end{align}

@@

\begin{theorem}
Fix the twisting datum $\alpha = \alpha_n$. The holomorphic twist of 4d $\cN=2$ super Yang--Mills with matter valued in a symplectic $\fg$-representation $U$ is perturbatively equivalent to the holomorphic BF theory with the space of fields $T^*[-1] \Sect(M, (U\otimes K_M^{1/2}[2n])\ham \fg)$. Moreover, the equivalence is $\MU(2)$-equivariant.
\label{thm:4d2holomorphictwist}
\end{theorem}
\begin{proof}
4d $\cN=2$ super Yang--Mills theory is obtained by dimensionally reducing 6d $\cN=(1,0)$ super Yang--Mills theory. Under dimensional reduction the 6d fields from Section \ref{sect:6dholomorphictwist} decompose as follows:
\begin{align*}
A_{1, 0}&\rightsquigarrow A_{1, 0}, \Tilde{a} \\
A_{0, 1}&\rightsquigarrow A_{0, 1}, a \\
B&\rightsquigarrow B, b \\
\rho&\rightsquigarrow \rho, \Tilde{\chi} \\
\psi & \rightsquigarrow \psi, \varsigma . \\
\end{align*}

@@

\section{Dimension 3}
The 3-dimensional $\mc N=k$ supersymmetry algebra has odd part $\Sigma \iso S \otimes W$, where $S$ is the 2-dimensional spinor representation of $\Spin(3) \iso \SU(2)$, and where $W$ is a $k$-dimensional vector space equipped with a bilinear pairing.  The maximal supersymmetric gauge theory has $\mc N=8$.  However, there are $\mc N=4$ super Yang-Mills theories for every choice $U$ of symplectic representation of the gauge group, and $\mc N=2$ super Yang-Mills theories for every choice $R$ of arbitrary representation of the gauge group.  In dimension 3, much like we saw in dimensions 5 and 7, all twisted theories can be obtained by dimensional reduction from theories one dimension higher.

\subsection{\texorpdfstring{$\cN = 2$}{N=2} Super Yang--Mills Theory}
\label{sect:3d_2_section}
We'll begin with the minimal super Yang-Mills theory that admits non-trivial twists (if $\mc N=1$ there are no square-zero supercharges).  So, fix a gauge group $G$, and a representation $R$.  The 3d $\mc N=2$ super Yang-Mills theory arises by dimensional reduction from $\mc N=1$ super Yang-Mills theory on $\RR^4$ with an $R$-valued chiral multiplet.  In this case, $W = \CC^2$ equipped with a nondegenerate symmetric bilinear pairing.

The R-symmetry group is $\spin(2;\CC) = \CC^\times$, acting on $W$ by the defining representation.

\vspace{-10pt}
\paragraph{Fields:} We can describe the BRST field content of $\mc N=2$ super Yang-Mills by restricting the 4d fields from Section \ref{sect:4d_1_section} to representations of the group $\spin(3;\CC)$.  The fields we obtain are
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and a scalar $\phi \in \Omega^0(\RR^3; \gg)$.
 \item matter bosons $(\Bar{\phi}, \phi) \in \Omega^0(\RR^3 ; R \oplus R^*)$.
 \item gauge fermions $\lambda \otimes u \in \Omega^0(\RR^3 ;  S \otimes W \otimes \fg)$.
 \item matter fermions $(\psi_-,\psi_+) \in \Omega^0(\RR^3 ; S \otimes R \oplus S \otimes R^*)$.
 \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

This theory admits a unique twist up to equivalence:
\begin{itemize}
 \item A square zero supercharge $Q \ne 0 \in \Sigma$ has two invariant directions.  There is a twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$, so the twisted theory carries a $U(1)$-action.
The twist is $\ZZ$-graded with $\alpha \colon \U(1) \hookrightarrow G_R$ given by the natural embedding. 
\end{itemize}

\subsubsection{Minimal Twist}
\label{sect:3dminimaltwist}
A square-zero supercharge $Q$ has rank 1, i.e. $Q = q \otimes w$ for some $w \in W$.  
We use the twisting homomorphism $\phi = (-)^{1/2} \colon \U(1)\hookrightarrow G_R$.

@@

\begin{theorem} \label{3d_minimal_twist_thm}
The minimal twist of 3d $\cN=2$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=2$ chiral multiplet valued in a representation $R$ is perturbatively equivalent to generalized $BF$ theory for the Lie algebra $\fg$ coupled to the generalized $\beta\gamma$ system with values in the representation $R$, with moduli space $T^*[-1]\mr{Map}(\CC \times \RR_{\mr{dR}}, R/\gg)$. Moreover this equivalence is $\mr U(1)$-equivariant.
\end{theorem}

\begin{proof}
By Theorem \ref{4d_minimal_twist_thm} the twist of 4d $\cN=1$ super Yang--Mills on $L\times N$ by $Q$ is perturbatively equivalent to the holomorphic Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N, R / \fg)$. By Proposition \ref{CS_diml_red_prop} we get that the dimensional reduction of holomorphic Chern--Simons on $L\times N$ along $\Re\colon N\rightarrow N_\RR$ is isomorphic to the generalized Chern--Simons theory with the space of fields $T^*[-1]\map(L\times N_\RR, R/\fg)$ and this isomorphism is $\mr U(1)$-equivariant by our choice of a twisting homomorphism.
\end{proof}

\subsection{\texorpdfstring{$\cN = 4$}{N=4} Super Yang--Mills Theory} \label{3d_4_section}
Next, consider 3d $\mc N=4$ supersymmetric Yang--Mills theory, which arises as the dimensional reduction of 4d $\mc N=2$ supersymmetric Yang--Mills theory; or equivalently by dimensional reduction of 6d $\mc N=(1,0)$ supersymmetric Yang--Mills theory. 
The $R$-symmetry group is $G_R = \Spin(4;\CC)$, acting on $W$ by the defining representation.

\vspace{-10pt}
\paragraph{Fields:}We can describe the BRST fields of $\mc N=4$ super Yang-Mills by restricting the 4d fields from Section \ref{4d_2_section} to representations of the group $\spin(3;\CC)$.  
The fields are:
\begin{itemize}
 \item gauge bosons $A \in \Omega^1(\RR^3; \gg)$, and three scalar fields $(\phi_1,\phi_2,\phi_3) \in \Omega^0(\RR^3; \gg \oplus \gg \oplus \gg)$.
 \item matter bosons $\phi \otimes v \in \Omega^0(\RR^3; W \otimes U)$.
 \item gauge fermions $(\lambda_1 \otimes u_1, \lambda_2 \otimes u_2) \in \Omega^0(\RR^3 ; S \otimes (W \oplus W) \otimes \gg)$.
 \item matter fermions $(\psi_1,\psi_2) \in \Omega^0(\RR^3; (S\oplus S) \otimes U)$.
 \item a ghost field $c \in \Omega^0(\RR^3; \gg)[1]$.
\end{itemize}

In the $\mc N=4$ supersymmetry algebra there are now three non-trivial orbits of square-zero supercharges.  An element $Q \in S \otimes W$ gives rise to a map $S^* \to W$; $Q$ squares to zero if its image is totally isotropic.  The classification of orbits includes the rank of this map.
\begin{itemize}
 \item Rank 1.  
 In this case $Q$ is minimal, with 2 invariant directions.  
 Such supercharges lie in a subalgebra isomorphic to the $\mc N=2$ supersymmetry algebra and are unique up to equivalence.
They admit a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading defined by a homomorphism $\alpha \colon \U(1) \to G_R$.
 \item Rank 2. Such supercharges are topological.  
A rank 2 supercharge defines a Lagrangian subspace of $W$, and therefore an orientation.  
The $G_R = \Spin(4;\CC)$-action factors through an $\SO(4)$ action on $W$, and so preserves orientation, so there are two $G_R$ orbits corresponding to the two choices of orientation.  
We refer to these as the $A$-twist and the $B$-twist, distinguished by whether or not they can be promoted to a twisting datum.
\begin{enumerate}
\item
An $A$-twist supercharge admits a twisting homomorphism $\phi \colon \U(1) \to G_R$ and a $\ZZ$-grading $\alpha \colon \U(1) \to G_R$.
\item
A $B$-twist supercharge admits the diagonal twisting homomorphism $\phi' \colon \SU(2) \to \SU(2) \times \SU(2) \to G_R$.  
This twist is only $\ZZ/2\ZZ$-graded
\end{enumerate}
\end{itemize}

@@

\begin{lemma} \label{3d_4_orbits_lemma}
A rank $(2,0)$ square 0 supercharge in the 4d $\mc N=2$ supersymmetry algebra restricts to an $A$-twisting supercharge in 3d $\mc N=4$.  Likewise a rank $(1,1)$ square zero supercharge in 4d $\mc N=2$ restricts to a $B$-twisting supercharge in 3d $\mc N=4$.
\end{lemma}

\begin{proof}
Let $W_4$ be the complex two-dimensional auxiliary space of the 4d $\cN=2$ supesymmetry algebra.
The projection from the 4d $\mc N=2$ supertranslation algebra to the 3d $\mc N=4$ supertranslation algebra induces an isomorphism $W_4 \oplus W_4^* \to W$ of representations of the group $\spin(3;\CC)$.  
This splits the fundamental representation $W$ into the sum of two Lagrangians, defining an orientation on $W$. 
A rank $(2,0)$ supercharge induces the Lagrangian subspace $W_4 \sub W$, which is oriented.  The corresponding twist can be promoted to a twisting datum using a copy of $\mr U(1)$ acting with weight 1 on $W_4$; explicitly, this is the homomorphism $\alpha \colon \U(1) \to G_R = \SL(2;\CC) \times \SL(2;\CC)$ given by the embedding into the second factor. 
This is the $A$-twist in our classification above.

A rank $(1,1)$ supercharges induces a Lagrangian subspace of the form $L \oplus L^* \sub W$, where $L$ is a 1-dimensional subspace of $W_4$.  This subspace has the opposite orientation, so corresponds to the $B$-twist in our classification above.  
\end{proof}

\subsubsection{Minimal Twist}
\label{sect:3d_4_minimal_twist}
Note that 3d $\cN=4$ supersymmetric Yang--Mills theory, viewed as a $\cN=2$ supersymmetric theory, coincides with 3d $\cN=2$ supersymmetric Yang--Mills theory with matter valued in the representation $R = U \oplus \gg$.

There is a unique twisting homomorphism $\phi \colon \U(1) \to \Spin(4;\CC)$ given by the restriction of the 4d $\cN=2$ twisting homomorphism for the minimal twist as in Theorem \ref{thm:4d2holomorphictwist} to the subgroup $\U(1) \subset \MU(2)$.

This twist also admits the following twisting datum.
To incorporate the $\ZZ$-grading, we use the twisting datum $\alpha \colon \mr U(1) \to \SU(2)_+ \times \SU(2)_- \iso G_R$.  The action of this $\alpha$ on $W$ coincides with the action of $\alpha_0$ in Section \ref{sect:4d_2_holomorphictwist} on the sum of the 4d auxiliary space with its dual $W_4 \oplus W_4^*$, composed with the isomorphism $W_4 \oplus W_4^* \to W$: indeed, both have weights $(1,1,-1,-1)$.  Therefore our equivalence is compatible with the $\ZZ$-grading in Theorem \ref{thm:4d2holomorphictwist} induced by $\alpha_0$.
%However, as in Section \ref{4d_2_section} we should take care: this identification is not R-symmetry equivariant.  Indeed, there is no choice of a 2-dimensional subspace $W' \sub W$, and an embedding $\mr O(2) \inj G_R = \Spin(4;\RR)$, making the map $W' \to W$ equivariant for the action of $\mr O(2)$ on $W'$ with weight 1.

\begin{theorem} \label{3d_4_minimal_twist_thm}
The minimal twist of 3d $\cN=4$ super Yang--Mills on $N \times L=\CC\times \RR$ is perturbatively equivalent to the generalized BF theory coupled to a higher holomorphic symplectic $U$-valued boson, with space of fields $T^*[-1]\mr{Sect}(N \times L_{\mr{dR}}, (U \otimes K^{1/2}_N) \ham \gg))$. Moreover, the equivalence is $\U(1)$-equivariant.
\end{theorem}
